Dynein project log

### 2016-09-17 thesis_stuff/thesis_stuff.tex
Minor modification to thesis_stuff.tex.

@@

>>>>

\section{Physical Parameters}
\subsection{Stalk and tail length}
Sarlah et. al use stalk and tail lengths of 12 and 14 nm, respectively. We used PyMol to examine the crystal structures 3VKH and XXXX (pre and post-powerstroke) to find
these values.

@@

\subsection{3D Pre/Post-PS structures, there are two Pre-PS states!}
Jianfeng Lin, Kyoko Okada, Milen Raytchev, Maria C. Smith \& Daniela Nicastro. ``Structural mechanism of the dynein power stroke.'' \textit{Nature Cell Biology} 2014. 16:479-485.

This paper finds the 3D structures of both pre (3J68) and post (3J67)-powerstroke dynein. This paper is about \textbf{axonmenal} dynein, which seems to be wildly different from cytoplasmic dynein, but this paper doesn't really mention any differences. The paper claims there are three conformational states: prestroke-1 immediately after MT unbinding, prestroke-2 after MT-binding, then poststroke after the powerstroke. This paper claims that transitioning between the post and pre-powerstroke ``resembled an opening jackknife with an angular amplitude of ~65$^{\circ}$ or ~50$^{\circ}$, depending on which axonemal dynein. It is unclear what this jackknife metaphor is referring to - the linker?. They make the claim that \textit{rotation of the head is the principle mechanism of Dynein powerstroke, not linker remodelling}. They seem to be claiming that the major thing differentiating the three states is the motor domain/head angle. It starts out facing the MT in post-stroke, then rotates away from the MT by 50-70 degrees into pre-1, then rotates towards the MT by 20 degrees to enter pre-2.\\

These figures show different measurements for equilibrium angles from the data in this paper:\\

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
    \caption{Post-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \hspace{5mm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
    \caption{Pre-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \label{fig:em_tomography_eq_angles}
\end{figure}
